The problem of protection of physical elements or information by limiting the access to only the relevant people is well known. The central challenge to the problem of security is the challenge of verifying the identity of a person trying to acquire access. The emergence of biometric techniques has induced an increasing interest in biometric-based security rather than knowledge-based or token-based security. This is mainly due to the fact  that the more traditional methods for security systems are easier breached or spoofed \citep{Ross2003}. Through the last decades researchers have investigated identity verification based on different biometric modalities. In the last decade investigations have been conducted in combining several biometric modalities in one system with the purpose of creating a system that performs better than the ones only utilising a single one. Results show that combining modalities performs better than any of the modalities separately \citep{Chen2005a}.  However, increased accuracy is not the only benefit of utilising multiple biometric traits. More modalities increases the universality of the system and decreases the influence of noisy measurements \citep{Ross2003}.

One of the fields where biometric-base security is increasingly applied is security for handheld devices such as smart phones. Although technology is advancing and mobile devices are equipped with still more advanced components, the computing power and the quality of the data from sensors, are both constraints of mobile devices. These limiting factors make it more challenging to make successful biometric-based identity verification on mobile devices rather than in other applications. \todo{add source?} Though the use of machine learning for image processing is well known, it has only scarcely been applied on data obtained by cameras on mobile devices. \cite{Khan2017a} presents different machine learning methods applied on iris images obtained by smart phone. \cite{Bazrafkan2017} applies deep learning for segmentation purposes on a database containing images acquired using a smart phone among others. 
 
\todo{describe more challenges (found in literature) before talking plan for solution}This work strives to make a system for identity verification based on multiple biometric traits for use on mobile devices. The biometric traits used are the iris and face. More specifically, this choice is made due to the arguments found in literature that iris is very distinctive, while face is non-invasive \citep{Wang2009a}. \hl{Furthermore, the application context of}  \todo{argue some more}