\section{Delay Requirements}\label{sec:reqDL}
\reqPrefix{DR}
The requirements for the delay based effects are set here. As delay is a part of several of the chosen effects this is set as a module with a main delay module incorporated in several different effects. 

\begin{requirement}\label{req:DL1}
	\requirement{The delay of the delay effects must stay within the limits set in \autoref{tab:delay_times}.}
	\argument{According to \autoref{tab:delay_times} the delay of the effects are usually in the scope of the delays presented.}
	\fullfilment{The delay of the effects are measured to be within the span of the delay effects presented. If these are within the set ranges, the requirement is fulfilled.}
\end{requirement}

\begin{requirement}\label{req:DL2}
	\requirement{The delay line of the flanger effect must be made with a variable delay.}
	\argument{The delay line of a flanger effect is typically varied according to a triangular or a sinusoidal waveform in the form of a \gls{lfo}.}
	\fullfilment{The delay of the flanger is modulated by a triangular or a sinusoidal waveform in the form of a \gls{lfo}, and the delay varies according to the amplitude of the \gls{lfo} and a fixed initial delay.}
\end{requirement}

\begin{requirement}\label{req:DL3}
	\requirement{The echo effect must have a variable decay.}
	\argument{It must be possible to adjust the decay of the amplitude of the delayed signal compared to the original signal, in order to dampen the echo and thus having an adjustable parameter in the effect.}
	\fullfilment{If the decay of the delayed signal is measured to be adjustable according to the original signal the requirement is fulfilled.}
\end{requirement}