\section{Other Effect Requirements}\label{sec:reqOR}
\reqPrefix{OR}
Any other requirements regarding the effects are presented in this section.

\begin{requirement}\label{req:OR1}
	\requirement{The equaliser must have a gain of $\pm \SI{12}{\deci\bel}$.}
	\argument{According to \cite{DAFX}, $\pm \SI{12}{\deci\bel}$ is a common gain factor in an equaliser.}
	\fullfilment{The frequency response of the equaliser is plotted at maximum and minimum gain, to see if the gain is $\pm \SI{12}{\deci\bel}$.}
\end{requirement}

\begin{requirement}\label{req:OR2}
	\requirement{The equaliser must operate in the entire audible frequency band.}
	\argument{Since the guitar produces frequencies across the entire audible frequency band, the equaliser must cover this entire band, in order to be able to attenuate or amplify the signal.}
	\fullfilment{The frequency response of the equaliser is plotted with no gain factor, and if there is no significant attenuation in the band after \SI{20}{\hertz} and before \SI{20}{\kilo\hertz}, the requirement is fulfilled.}
\end{requirement}

\begin{requirement}\label{req:OR3}
	\requirement{It must be possible to change the bandwidth and the center frequency in the equaliser's band pass filters.}
	\argument{In order to vary the amplitude throughout the entire frequency band, it must be possible to change the center frequency and the bandwidth of the filters.}
	\fullfilment{If it is possible to change the center frequency and the bandwidth of the band pass filters in the equaliser, the requirement is fulfilled.}
\end{requirement}