\section{Quality Requirements}\label{sec:reqQR}
\reqPrefix{QR}
As the \gls{dsp} board has requirements regarding input signal and to ensure a certain general quality of the signals, a set of requirements are established. These are presented in this section.

\begin{requirement}\label{req:qr1}
	\requirement{The \gls{snr} of the \gls{preamp} must be greater than the \gls{snr} of the output of the \gls{dsp}, when a signal is sent straight through.}
	\argument{In order to reduce noise the \gls{preamp} must have a greater \gls{snr} than what is measured at the output of the \gls{dsp}.}
	\fullfilment{The \gls{snr} of the \gls{preamp} is calculated and measured to have a ratio greater than what is measured through the \gls{dsp}.}
\end{requirement}\label{req:SNratio}

\begin{requirement}\label{req:qr2}
	\requirement{The sample frequency must be \SI{44.1}{\kilo\hertz}.}
	\argument{The human hearing spans from \SI{20}{\hertz} to \SI{20}{\kilo\hertz}, and as stated in \autoref{sec:guitar_analysis} a standard tuned guitar can produce frequencies throughout this spectrum. According to the Nyquist criterion the sample rate should be at least twice the input frequency. As \SI{44.1}{\kilo\hertz} is a heavily used sample frequency, this is chosen \citep{sample_rate}.}
	\fullfilment{If implemented requirement is fulfilled.}
\end{requirement}

\begin{requirement}\label{req:qr3}
	\requirement{The input voltage must not exceed \SI{0.9}{\volt} peak.}
	\argument{According to the datasheet of the audio \gls{codec} on the \gls{dsp} board, the maximum rating for the input voltage is \SI{0.9}{\volt} peak \citep{dspadc}.}
	\fullfilment{As long as the input signal does not exceed \SI{0.9}{\volt} the requirement is fulfilled. This can be controlled with an amplifier before the input.}
\end{requirement}

\begin{requirement}\label{req:qr4}
	\requirement{The input impedance of the system must be at least \SI{1}{\mega\ohm}.}
	\argument{Since the output impedance of the guitar, measured in \autoref{ch:guitar_meas}, is close to \SI{100}{\kilo\ohm}. To minimise signal loss the relation between output- and input impedance must be at least 10 to 1.}
	\fullfilment{The input impedance of the system is measured. If this is equal to \SI{1}{\mega\ohm} or higher the requirement is fulfilled.}
\end{requirement}
