\section{User Interface Requirements}\label{sec:reqUI}
\reqPrefix{UIR}
To ease the user experience with the effect board a \gls{ui} is needed. This enables the user to select the desired effect and set effect parameters. Requirements for these functions are presented in this section.

\begin{requirement}\label{req:UI1}
	\requirement{The effect board must have a \gls{ui}.}
	\argument{To ease the use of the effect board and enable the user to choose and manipulate the effects a \gls{ui}.}
	\fullfilment{If implemented requirement is fulfilled.}
\end{requirement}\label{req:UIreq}

\begin{requirement}\label{req:UI2}
	\requirement{The \gls{ui} must have an effect selection menu, including effect setup.}
	\argument{To avoid loading a new program for each effect, an effect selection menu is more desirable to a user.}
	\fullfilment{If implemented requirement is fulfilled.}
\end{requirement}\label{req:UImenu}

\begin{requirement}\label{req:UI3}
	\requirement{The \gls{ui} must have four external buttons and a screen.}
	\argument{The user needs a physical interface to operate the effects board.}
	\fullfilment{If implemented requirement is fulfilled.}
\end{requirement}\label{req:UIphys}

\begin{requirement}\label{req:UI4}
	\requirement{It must be possible to configure each effect independently.}
	\argument{The user must be able to configure an effect and its parameters without this affecting the other effects.}
	\fullfilment{If implemented requirement if fulfilled.}
\end{requirement}\label{req:UIconf}